Water Management

### 2020-01-16 Paper/paper.tex
biber -> bibtex
introduction changes

% packages used for citations
\usepackage[
backend=biber,
style=alphabetic,
citestyle=authoryear,
natbib=true
]{biblatex}
\addbibresource{collection.bib}

@@

At the end of the year, water in the reservoir is replenished by rainfall, which we assume to be randomly following a lognormal distribution: %Evtl Zitat: https://www.waterlog.info/pdf/freqtxt.pdf
\begin{equation}
	r \sim lognormal(\mu, \sigma^2)
\end{equation}

@@

>>>>

% packages used for citations
\usepackage[
backend=bibtex,
style=alphabetic,
citestyle=authoryear,
natbib=true
]{biblatex}
\addbibresource{collection.bib}

@@

At the end of the year, water in the reservoir is replenished by rainfall, which we can assume to be randomly following a lognormal distribution \citep{oosterbaan1994frequency}:
\begin{equation}
	r \sim lognormal(\mu, \sigma^2)
\end{equation}

@@

Using dynamic programming...
